\documentclass[conference]{IEEEtran}

\usepackage{epsfig}
\usepackage{url}
\usepackage{cite}
\usepackage{fancybox}
\usepackage{graphicx}
\graphicspath{{images/}}

\begin{document}
\title{Strategies to Combat Administrator Threats to Cloud Computing Systems}
\author{
  \IEEEauthorblockN{Eric Adamski}
  \IEEEauthorblockA{
    School of Computer Science\\
    Carleton University\\
    Ottawa, Ontario, Canada \\
    Email: \{eric.adamski@cmail.carleton.ca\}
  }
  \and
  \IEEEauthorblockN{Shivjot Baidwan}
  \IEEEauthorblockA{
    Ottawa Carleton Institute of Computer Science \\
    University of Ottawa\\
    Ottawa, Ontario, Canada \\
    Email: \{sbaid017@uottawa.ca\}
  }
}

\maketitle

\begin{abstract}
  Cloud services are becoming increasingly popular in the world of technology, as more and more people have come to rely on these services to store personal and private data. Who is to say that the organizations which give cloud based commodities are dependable and secure ? Cloud service providers use techniques such as, data encryption, and cloning for protecting themselves against outside attacks, but individually these techniques lack immunity from the company employees, the insiders. The most essential way which ought to be utilized for protection against threats can be executed at the physical level by having a sturdy infrastructure. It does not do much by itself but it forms the foundation of the strategies to curb the threats, in particular the insider threats. The other strategies which lie atop a solid infrastructure are cloning, encryption, migration, deletion. Throughout the paper we are going to talk about models based on these techniques, how they are applied to conventional computing threats and how this differs from threats to cloud software. This paper will review how modern systems utilize the strategical models previously discussed. In specific we will discuss how these models can be utilized to protect against insider threats.
\end{abstract}

\IEEEpeerreviewmaketitle

%% Shivu's Stuff %
\input{sections/introduction}
\input{sections/problem_defenition}
\input{sections/background}
%%===============%
%% Eric's Stuff  %
\input{sections/solution}
\input{sections/conclusion}
%%===============%


\bibliographystyle{IEEEtran}
\bibliography{refs}

\end{document}
