\section{Introduction}

All through the history of computer science, various endeavors have been attempted to
disassociate users from the needs related to computer hardware and from the time sharing
services foreseen in 1960s, mesh of systems in the 1990s to the economic network systems of
the contemporary era. This reflection is relentlessly turning into a reality as various business
and educational pioneers related to this sphere of science are soaring towards the Cloud
Computing.\cite{jensen}
Cloud computing is a metaphor related to computer science, which progressed in the late
2000s, and it rests on the practicality and the dispersion of the computer resources. It
comprises of expanding groups of distant servers and the programming networks which permit
a number of various types of information sources to be uploaded for real time processing in
order to achieve computing outcomes unaccompanied by the necessity to accumulate
processed information on the cloud. Cloud computing is fundamentally a network-based
domain that lays emphasis on the sharing of various resources and computations. In reality, the
clouds are associated with not only the applications expressed as services over the Internet but
also the Software and the Hardware prevailing in the data centres which are responsible for
providing these services.\cite{sabahi} Tremendous scalability and adaptability, minimization of the
expenses and fundamentally the service on demand capabilities are few of the crucial factors,
which have popularized cloud computing.
There are also a number of vital strategy issues in relation to cloud computing, incorporating
the issues of security, privacy, anonymousness, reliability, government surveillance and many
more. However, the paramount among them is the issue of security and additionally how the
cloud service provider administers it to the users. Broadly Cloud Computing has a number of
clients, for instance, regular users, the educated community and the business firms and all
having diverse motivations for relocating to the cloud.  For all of them the issue related to
security of the data stored on the cloud is a vital one. All the cloud-computing users are deeply
concerned about any type of attacks, which can comprise the confidentiality, and the integrity
of the data.\cite{kandias}
There are various security concerns for cloud computing as they envelop a number of
advancements which include the systems, databases, operating systems, resource planning,
balancing of load, memory administration as well as concurrency control.  Subsequently,
security issues for a hefty amount of these systems and innovations are relevant to cloud
computing. For instance, the system accountable for the interconnection between a numbers
of systems must be secure. Moreover, mapping the virtual machines to the physical machines
needs to be completed securely.\cite{sen}
The cloud computing service providers use strategies for instance, data encryption and cloning
in order to ensure themselves and the services they provide against the outside assaults,
nonetheless all these techniques and methods require invulnerability from the representatives
of the organization which are the insiders.
Out of a number of attacks which can happen against the data stored in a cloud such as data
breach, data loss, service traffic hijacking, insecure APIs, denial of service, physical attacks,
overuse and abuse of cloud services, issues related to shared technology and many more, this
literature survey is more focused on the attacks by the malicious insiders also known as the
insider attacks and the various types of defensive mechanisms against the malicious insiders
who work or have worked for the cloud.
Although the research community has concentrated on a number of features associated with
the cloud computing security essentially the authentication and authorization, storage of data
in a secure and trustworthy manner, digital forensics, and additionally the legitimate challenges
as well. But still, the issue of the insider danger correlated to the insider as of now hasn’t been
provided visible focus of research.  The conventional threat related to the insiders has been
consistently under study and research for over a decade. Though it is seen as a complex issue
but still there are numerous methodologies in order to depreciate it.\cite{kandias}
